Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-06-29 analysis/paper/paper.Rmd
Added schedule outline to test

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```
# schedule outline
Schedule:
Breakdown –
July
-          6 pages (3 single)// 1500w BM
-          section from background “what is…” 200w PS
-          section from background “what are scholars saying about it…” 400w PS
August
-          6 pages (3 single)// 1500w BM
-          continue section from background “what are scholars saying about it…” 400w PS
September
-          6 pages (3 single)// 1500w BM
-          continue editing section PS
-          Complete 1st draft before sept. 26th, UW term begins. Preferably by 19th, one week before to avoid overlapping.
October
-          Continue building to target word count BM/PS
-          Complete 2nd draft by end of October
November
-          Continue editing, complete 3rd draft by date TBD
